\Title

### 2015-11-02 manuscript.tex
About notebooks and where to find code

The computational experiments
(e.g., data processing, synthetic tests, real data application)
were performed in
Jupyter (formerly IPython) notebooks
\citep[][ \url{http://jupyter.org/}]{perez2007}.

>>>>

The computational experiments
(e.g., data processing, synthetic tests, real data application)
were performed in
Jupyter (formerly IPython) notebooks
\citep[][ \url{http://jupyter.org/}]{perez2007}.
The notebook files combine the source code used to run the experiments,
the results and figures generated by the code,
and rich text to explain and document the analysis.

The Python implementation of the inversion as well as the Jupyter notebooks are
freely available under the terms of the BSD 3-clause open-source license.
Both can be found at the online repository
\url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}.
An archived version is also available at
\url{http://dx.doi.org/DOI_HERE} (made available upon publication).
\todo{Insert Zenodo DOI here}
